A Middleware for Symmetric Peer-to-Peer Applications

### 2023-03-12 tpds-23/tpds-23.tex
...

Our middleware is written in C and relies on the library \emph{SDL}%
\footnote{SDL: \url{http://www.libsdl.org}}
to deal with the network, timers, and input events, such as mouse clicks and
key presses.
The full source code%
\footnote{Code: \url{http://github.com/TODO-hidden-blind-review}}
is under 500 lines of code.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{move}
    \caption[XXX] {
        \textbf{An application example:}
        A moving rectangle is controlled by peers connected indirectly.
        Users can press \code{↑ ↓ → ←} to change the direction of the
        rectangle or \code{SPACE} to pause the application.
        The inputs are applied simultaneously in all peers, as if they were
        mirrors of a single application.
        Video: \url{http://youtube.com/TODO-hidden-blind-review}
        \label{fig.move}
    }
\end{figure}

@@

Considering goal (a), we need to take a closer look at Figure~\ref{fig.baks}.
The color patterns indicate clear boundaries for the scenarios that can meet
event deadlines with the desired performance.
%
For instance, high event deadlines (column $5x$) make all scenarios viable,
even with high latencies and event frequencies.
As an application example, chats are not affected by higher event deadlines.
Nevertheless, the lower is the deadline, the less applications suit the
middleware.
%
For the lowest possible $\Delta$ (column $1x$), we see that the middleware can
either handle low latencies with high event frequencies (e.g., $5ms$ with
$100evt/min$) or high latencies with low event frequencies (e.g., $100ms$ with
$5evt/min$).
%
The middleware does not perform well under higher network latencies (e.g., over
$250ms$).
This is expected since peers that are multiple hops away take too long to
synchronize past events and may generate future events in the meantime, which
causes time travels.
%
In summary, the color patterns in the table provide the necessary information
to confront an application with its feasibility or desired performance.

@@

%\begin{comment}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{chico}}]{Francisco Sant'Anna}
received his PhD degree in Computer Science from PUC-Rio, Brazil in
2013.
In 2016, he joined the Faculty of Computer Science at the Rio de Janeiro State
University, Brazil.
His research interests include Programming Languages and Concurrent \&
Distributed Systems.
\end{IEEEbiography}
%\end{comment}

>>>>

Our middleware is written in C and relies on the library \emph{SDL}%
\footnote{SDL: \url{http://www.libsdl.org}}
to deal with the network, timers, and input events, such as mouse clicks and
key presses.
The full source code%
\footnote{Code: \url{http://github.com/fsantanna/p2p-tml/}}
is under 500 lines of code.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{move}
    \caption[XXX] {
        \textbf{An application example:}
        A moving rectangle is controlled by peers connected indirectly.
        Users can press \code{↑ ↓ → ←} to change the direction of the
        rectangle or \code{SPACE} to pause the application.
        The inputs are applied simultaneously in all peers, as if they were
        mirrors of a single application.
        Video: \url{https://youtu.be/zkl0vSOGino}
        \label{fig.move}
    }
\end{figure}

@@

Considering goal (a), we need to take a closer look at Figure~\ref{fig.baks}.
The color patterns indicate clear boundaries for the scenarios that can meet
event deadlines with the desired performance.
%
For instance, high event deadlines (column $5x$) make all scenarios viable,
even with high latencies and event frequencies.
As an application example, chats are not affected by higher event deadlines.
Nevertheless, the lower is the deadline, the less applications suit the
middleware.
%
For the lowest possible $\Delta$ (column $1x$), we see that the middleware can
either handle low latencies with high event frequencies (e.g., $5ms$ with
$100evt/min$) or high latencies with low event frequencies (e.g., $100ms$ with
$5evt/min$).
Note that the middleware cannot ensure \emph{instantaneity} for events in most
scenarios, which would require a very low $\Delta$~\cite{melding}.
%
The middleware does not perform well under higher network latencies (e.g., over
$250ms$).
This is expected since peers that are multiple hops away take too long to
synchronize past events and may generate future events in the meantime, which
causes time travels.
%
In summary, the color patterns in the table provide the necessary information
to confront an application with its feasibility or desired performance.

@@

\begin{comment}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{chico}}]{Francisco Sant'Anna}
received his PhD degree in Computer Science from PUC-Rio, Brazil in
2013.
In 2016, he joined the Faculty of Computer Science at the Rio de Janeiro State
University, Brazil.
His research interests include Programming Languages and Concurrent \&
Distributed Systems.
\end{IEEEbiography}
\end{comment}
